FEM Model Analysis

### 2021-06-24 FEM_R/dfly_detailed_output.Rmd
Lots of little changes getting ready to submit the paper to IJM

theme('minimal')
```

Setup is complete (including the working directory), so let's read in some of the data files.

@@

```{r}
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_append.dta')
heart <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_append.dta')
smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_append.dta')
```

@@

# generate flag for initial wave with disease and year died (if known)
new <- cohort %>%
          group_by(hhidpn, mcrep, year) %>%

@@

aData <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/input_data/detailed_output/tot/base_treated_merged_smoken_tot.dta')

@@

>>>>

rm(workingDir)
```

Setup is complete, so let's read in some of the data files.

@@

```{r}
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_append.dta')
#heart <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_append.dta')
smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_append.dta')
```

@@

# generate flag for initial wave with disease and year died (if known)
new.c <- cohort %>%
          group_by(hhidpn, mcrep) %>%
          arrange(year, .by_group = TRUE) %>%
          mutate(hearte_init = min(year[hearte == 1]), hearte_died = max(year[hearte == 1])) %>%
          mutate(lunge_init = min(year[lunge == 1]), lunge_died = max(year[lunge == 1]))

# Replace all infinite values with 0 (infinites generated in mutate calls above)
new$hearte_init[is.infinite(new$hearte_init)] <- 0
new$hearte_died[is.infinite(new$hearte_died)] <- 0
new$lunge_init[is.infinite(new$lunge_init)] <- 0
new$lunge_died[is.infinite(new$lunge_died)] <- 0

# now generate flag variable if

#rm(new)
```

## Using output from stata script treatment_on_treated.do or some version of it

aData <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/input_data/detailed_output/tot/base_treated_merged_smoken_tot_test.dta')

@@

### Whole Population
```{r}

all <- aData %>%
        summarise(improv.ly = mean(improved_lifeyears), improv.dfly = mean(improved_dflys))

all

@@

```{r}
all2 <- aData %>%
          summarise(base.ly = mean(total_lifeyears_basecase), int.ly = mean(total_lifeyears),
                    base.dfly = mean(total_dflys_basecase), int.dfly = mean(total_dflys))

all2
```

### By Education
```{r}

### 2021-06-24 FEM_R/model_analysis_core.Rmd
Lots of little changes getting ready to submit the paper to IJM

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/"
knitr::opts_knit$set(root.dir = workingDir)

@@

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CV2/ELSA_CV2_summary.dta')

@@

#AgeUK
male_au <- read.csv('../../Validation/AgeUK-chronDisease-MALE.csv')
female_au <- read.csv('../../Validation/AgeUK-chronDisease-FEMALE.csv')

@@

# Function to filter the combined dataset and visualise
visAgeUKValid <- function(data, cd, gender, path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/Validation/ageUK/') {

@@

ggsave(filename = 'smoking_prev_2018.png',
       plot = smok.plot,
       path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/Validation/',
       width = 7,
       height = 5)

>>>>

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/COMPLETE/"
knitr::opts_knit$set(root.dir = workingDir)

@@

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CV2/ELSA_CV2_summary.dta')

@@

#AgeUK
male_au <- read.csv('../../../Validation/AgeUK-chronDisease-MALE.csv')
female_au <- read.csv('../../../Validation/AgeUK-chronDisease-FEMALE.csv')

@@

# Function to filter the combined dataset and visualise
visAgeUKValid <- function(data, cd, gender, path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/ageUK/') {

@@

ggsave(filename = 'smoking_prev_2018.png',
       plot = smok.plot,
       path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/',
       width = 7,
       height = 5)
